Comprehensive Quality Awareness Automated Semantic Web Service Composition

### 2017-03-23 paper.tex
update

We observe an interesting pattern from Table \ref{decisionTable}. The mean values of $QoS$ using QoS evaluation model are significantly higher than those using comprehensive quality evaluation model for Task 2, 3, 4 and 5,  but the mean value of $MT$ and $S$ using comprehensive quality evaluation model are consistently significantly higher than those using QoS evluation model for all tasks with a slight trade-off in $QoS$.

\begin{table}[]
\footnotesize
\centering
\caption{Mean values of $MT$, $S$, and $QoS$ for QoS Evaluation Model and Comprehensive Quality Evaluation Model using PSO-based approach}
\label{decisionTable}
\begin{tabular}{l|l|l|l}
\hline
\multicolumn{2}{c|}{WSC09}              & QoS Evaluation Model         &\shortstack{Comprehensive \\ Quality Evaluation Model} \\ \hline
\multirow{3}{*}{Task1}  &$MT$   &0.189787 $\pm$ 0.039278686            &0.221862 $\pm$ 0.009582 $\uparrow$ \\ \cline{2-4} 
                        &$S$    &0.884962 $\pm$ 0.014140               &0.894082 $\pm$ 0.009206 $\uparrow$ \\ \cline{2-4}
                        &$QoS$  &0.278730 $\pm$ 0.007786               &0.280222 $\pm$ 0.008212                          \\ \hline
\multirow{3}{*}{Task2}  &$MT$   &0.001795 $\pm$ 0.000719               &0.001977 $\pm$ 0.001566 $\uparrow$ \\ \cline{2-4} 
                        &$S$    &0.906971 $\pm$ 0.005855               &0.923970 $\pm$ 0.006898 $\uparrow$   \\ \cline{2-4}
                        &$QoS$  &0.239979 $\pm$ 0.000578 $\uparrow$    &0.238596 $\pm$ 0.001264 \\ \hline
\multirow{3}{*}{Task3}  &$MT$   &0.158526 $\pm$ 0.014028               &0.245830 $\pm$ 0.007761 $\uparrow$   \\ \cline{2-4} 
                        &$S$    &0.949109 $\pm$ 0.002331               &0.972765 $\pm$ 0.002980 $\uparrow$           \\ \cline{2-4}
                        &$QoS$  &0.247002 $\pm$ 0.000661 $\uparrow$    &0.245631 $\pm$ 0.000431            \\ \hline
\multirow{3}{*}{Task4}  &$MT$   &0.000000 $\pm$ 0.000000               &0.000004 $\pm$ 0.000002 $\uparrow$ \\ \cline{2-4} 
                        &$S$    &0.879514 $\pm$ 0.007456               &0.920733 $\pm$ 0.000001 $\uparrow$ \\ \cline{2-4}
                        &$QoS$  &0.242297 $\pm$ 0.000507 $\uparrow$    &0.236677 $\pm$ 0.002211  \\ \hline
\multirow{3}{*}{Task5}  &$MT$   &  0.000042 $\pm$ 0.000030             &0.000078 $\pm$ 0.000020 $\uparrow$           \\ \cline{2-4} 
                        &$S$    &  0.915933 $\pm$ 0.012888             &0.927678 $\pm$ 0.002578 $\uparrow$                 \\ \cline{2-4}
                        &$QoS$  & 0.238189 $\pm$ 0.000240 $\uparrow$      &  0.237485 $\pm$  0.000328  \\ \hline                                                   
\end{tabular}
\end{table}

@@

\begin{figure}[h]
\centering{
\fbox{
\includegraphics[scale=.22]{comparisontest.pdf}}}
 \caption{Example Comparison of solutions to Task 3 using two different evaluation model.}
 \label{comparisontest}
\end{figure}

>>>>

We observe an interesting pattern from Table \ref{decisionTable}. The mean values of $QoS$ using QoS evaluation model are significantly higher than those using comprehensive quality evaluation model for Task 2, 3, 4 and 5,  but the mean value of $MT$ and $S$ using comprehensive quality evaluation model are consistently significantly higher than those using QoS evaluation model for all tasks with a slight trade-off in $QoS$.

\begin{table}[]
\footnotesize
\centering
\caption{Mean values of $SM$ and $QoS$ for QoS Evaluation Model and Comprehensive Quality Evaluation Model using PSO-based approach}
\label{decisionTable}
\begin{tabular}{l|l|l|l}
\hline
\multicolumn{2}{c|}{WSC09}              & QoS Evaluation Model         &\shortstack{Comprehensive \\ Quality Evaluation Model} \\ \hline
\multirow{2}{*}{Task1}  &$SM$   &0.537375 $\pm$ 0.026709               &0.557972 $\pm$ 0.009394 $\uparrow$ \\ \cline{2-4}
                        &$QoS$  &0.557460 $\pm$ 0.015572               &0.560444 $\pm$ 0.016424                          \\ \hline
\multirow{2}{*}{Task2}  &$SM$   &0.454383 $\pm$ 0.003287               &0.462974 $\pm$ 0.004232 $\uparrow$ \\ \cline{2-4} 
                        &$QoS$  &0.479958 $\pm$ 0.001156 $\uparrow$    &0.477192 $\pm$ 0.002528 \\ \hline
\multirow{2}{*}{Task3}  &$SM$   &0.553818 $\pm$ 0.008180               &0.609298 $\pm$ 0.005371 $\uparrow$   \\ \cline{2-4} 
                        &$QoS$  &0.494004 $\pm$ 0.001322 $\uparrow$    &0.491262 $\pm$ 0.000862            \\ \hline
\multirow{3}{*}{Task4}  &$SM$   &0.439757 $\pm$ 0.003728               &0.460369 $\pm$ 0.000002 $\uparrow$ \\ \cline{2-4} 
                        &$QoS$  &0.484594 $\pm$ 0.001014 $\uparrow$    &0.473354 $\pm$ 0.004422  \\ \hline
\multirow{3}{*}{Task5}  &$SM$   &0.457988 $\pm$ 0.006459               &0.463878 $\pm$ 0.001299 $\uparrow$           \\ \cline{2-4} 
                        &$QoS$  &0.476378 $\pm$ 0.000480 $\uparrow$    &0.474970 $\pm$ 0.000656  \\ \hline                                                   
\end{tabular}
\end{table}

@@

\begin{figure}[h]
\centering{
\fbox{
\includegraphics[scale=.29]{comparisontest.pdf}}}
 \caption{Example Comparison of solutions to Task 3 using two different evaluation model.}
 \label{comparisontest}
\end{figure}
